---
title: 'Homework 1 Question 2'
author: 'Yuval Saraf'
date: '3/29/2020'
output: html_document
---
#### Preparation

```{r}
nflSalaries = read.csv('NFL-salaries.csv');
nflSalaries$SalaryNum = as.numeric(stringr::str_remove(nflSalaries$Salary, '\\$'));
summary(nflSalaries);
```
1. Find the subset of players that earned at least $1,000,000. Assign those rows to the variable BigBucks.
    ```{r}
        minForBigBucks = 10^6;
        BigBucks = nflSalaries[nflSalaries$SalaryNum >= minForBigBucks, ];
        summary(BigBucks)
    ```
    a. How many players are on this list? 
        ```{r}
        nrow(BigBucks);
        ```
    b.  
        Draw a histogram of the salaries of the Players in the BigBucks category.
        * In order to improve the readability of the histogram, scale the data so that the salaries are in millions of dollars. For example, Cousins earned $27,500,000. You would depict this as 27.5.
        * Of course, you need to provide an appropriate label for the x-axis so that it is clear that this is $ 27.5M and not twenty-seven dollars and 50 cents
        * Set the number of bins in the histogram to 5 using the “breaks” parameter. (use ‘?hist’ for details)
        * Save the plot to a PDF
        * Open the PDF file to make sure that you succeeded.
        <br>
        <br>
        ```{r, message=FALSE}
        desiredBins = 5;
        nflSalariesInMillions = BigBucks$SalaryNum / 10^6;
        minSalaryInMillions = min(nflSalariesInMillions);
        maxSalaryInMillions = max(nflSalariesInMillions);

        xaxis = seq(from = minSalaryInMillions, to = maxSalaryInMillions, length.out = desiredBins + 1);

        drawHist <- function() {
            hist(
                nflSalariesInMillions,
                xaxt = 'n',
                main = 'Histogram of NFL Salaries',
                xlab = expression('NFL salaries'['[M$]']),
                ylab = 'Count',
                breaks = xaxis
            );
            axis(1, at = xaxis);
        }

        pdf('histogram-NFL-salaries.pdf');
        drawHist();
        suppressMessages <- dev.off();

        drawHist();
        ```
2. Analyze the entire dataset to find out how many players make the lowest salary. Start by finding the minimum salary and find those players that make that minimum salary.

    ```{r}
    minSalary = min(nflSalaries$SalaryNum);
    minBucks = nflSalaries[nflSalaries$SalaryNum == minSalary, ];
    nrow(minBucks);
    minBucks
    ```

3. How many players earn more than 10 million? 

    ```{r}
    superBigBucks = nflSalaries[nflSalaries$SalaryNum >= 10 * 10^6, ];
    nrow(superBigBucks);
    ```